---
output: github_document
---

[![Travis-CI Build Status](https://travis-ci.org/jtrecenti/music21.svg?branch=master)](https://travis-ci.org/jtrecenti/music21)

<!-- README.md is generated from README.Rmd. Please edit that file -->

**Under development. Please contribute.**

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# music21

The goal of `music21` is to have an pipe-able API of [music21 python library](http://web.mit.edu/music21/doc/index.html). It uses RStudio's excellent [`reticulate`](https://github.com/rstudio/reticulate) package in the backend.

In practice, `music21` is more limited than the python library. However, it is really easy to run any functions from `music21` inside R.


## Installation

You can install `music21` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jtrecenti/music21")
```

## `music21` object

```{r}
library(music21)
music21
```

`music21` object stores the python module. It is possible to run any function from it just by using `$`, treating it as a Reference Class object.

```{r, results="asis"}
note <- music21$note$Note("C#")
note
```

```{r note, fig.width=2, fig.height=1.5}
note %>% 
  plot()
```

## Example

### Show bach chorales

```{r message=FALSE}
get_composer("bach") %>% 
  head()
```

Let's get one of these paths and read:

```{r}
bach_music <- get_composer("bach")[61] %>% 
  read_music()
```

### Plot bwv165.6 music

Now let's plot the music!

```{r bach, fig.width=6, fig.height=5}
bach_music %>% 
  plot()
```

In RStudio, you can use the `view` function to see the music inside viewer pane.

### Print bwv165.6 music (soprano part)

```{r}
bach_music[[1]]
```




